---
title: "example plot function"
output: html_document
---

# Set up
```{r setup, include=FALSE}
library(tidyverse)

```

## Read in data
```{r}
pgrdata_Awareness <-  read_csv(here::here("Data", "processed", "pgrdata_Awareness.csv"))
```


Ok, let's have a look at some data

```{r}
pgrdata_Awareness
```

# Try plotting
Let's set up the response levels

```{r}
response_levels <- c(
  "Practicing myself",
  "Accessing / using only",
  "Aware only",
  "Not aware / not sure if applicable",
  "Not applicable"
)
```

## Basic bar chart of answers across everything
```{r}
count_by_answer_across_all <- pgrdata_Awareness %>% 
  group_by(Answer) %>%
  summarise(num_respondents = sum(n, na.rm = TRUE)) %>% 
  mutate(Answer = factor(Answer, levels = response_levels))
  
count_by_answer_all %>% 
  ggplot() +
    geom_bar(aes(x = Answer, y = num_respondents), stat = "identity")
  
```

## Basic bar chart where fill shows number answers by division
```{r}
count_by_answer_and_div <- pgrdata_Awareness %>% 
  group_by(Answer, Div) %>%
  summarise(num_respondents = sum(n, na.rm = TRUE)) %>% 
  mutate(Answer = factor(Answer, levels = response_levels))

count_by_answer_and_div %>% 
  ggplot() +
    geom_bar(aes(x = Answer, y = num_respondents, fill = Div), stat = "identity")
```

it's super clear that we've got a very low number of responses from conted compared to the other divisions

## Same chart again, but facetted by question
```{r}
count_by_answer_and_div_and_orp <- pgrdata_Awareness %>% 
  group_by(Answer, Div, LabelIndiv) %>%
  summarise(num_respondents = sum(n, na.rm = TRUE)) %>% 
  mutate(Answer = factor(Answer, levels = response_levels))

count_by_answer_and_div_and_orp %>% 
  ggplot() +
    geom_bar(aes(x = Answer, y = num_respondents, fill = Div), stat = "identity") +
    facet_wrap(~LabelIndiv)
```


## Let's make fill the awareness level and facetting the div
```{r}
count_by_answer_and_div_and_orp %>% 
  ggplot() +
    geom_bar(aes(x = LabelIndiv, y = num_respondents, fill = Answer), stat = "identity") +
    facet_wrap(~Div)
```

## Let's make the bars even height and set a better color scheme
```{r}
answers_colors <- c("#ABDDA4", "#FFFFBF", "#FDAE61", "#D7191C", "black")

count_by_answer_and_div_and_orp %>% 
  ggplot() +
    geom_bar(aes(x = LabelIndiv, y = num_respondents, fill = Answer), stat = "identity", position = "fill") +
    facet_wrap(~Div) +
    scale_fill_manual(values = answers_colors)
```

## Let's flip it and have a single column 
```{r}
count_by_answer_and_div_and_orp %>% 
  ggplot() +
    geom_bar(aes(x = LabelIndiv, y = num_respondents, fill = Answer), stat = "identity", position = "fill") +
    scale_fill_manual(values = answers_colors) +
    coord_flip() +
    facet_wrap(~Div, ncol = 1)
    
```
This is the first useful version - it allows us to easily glance across the different departments

## Let's make the facetting ORP type instead
```{r}
count_by_answer_and_div_and_orp %>% 
  ggplot() +
    geom_bar(aes(x = Div, y = num_respondents, fill = Answer), stat = "identity", position = "fill") +
    scale_fill_manual(values = answers_colors) +
    coord_flip() +
    facet_wrap(~LabelIndiv, ncol = 1)
    
```

This is the second plot - I think this is probably the better one than the one before, because the focus is probably not meant to be on comparing the divisions but rather on comparing the ORPs.

It takes up a bunch of space but I would retain a one-column layout because you can then easily with your eye do the comparison.

### Iterate on this plot
Let's make the theme minimal, turn the scale into a percentage scale, remove the x and y labels, and increase the font size of the facet wrapping labels

(we might want to also order the division by who has the highest proportion of open practices - this is a bit fiddly to do when we're also doing facet wrapping, but it's possible. There's a useful guide here: https://juliasilge.com/blog/reorder-within/ )


```{r}
count_by_answer_and_div_and_orp %>% 
  ggplot() +
    geom_bar(aes(x = Div, y = num_respondents, fill = Answer), stat = "identity", position = "fill") +
    scale_fill_manual(values = answers_colors) +
    facet_wrap(~LabelIndiv, scales = "free_x", ncol = 1) +
    coord_flip() +
    theme_minimal() +
    scale_y_continuous(labels = scales::percent) +
    theme(legend.title = element_blank(),
          strip.text.x = element_text(size = 10, colour = "black")) +
    labs(x = "", y = "")

ggsave("figures/example-plot.png", height = 8)
```