---
title: "RROx survey: Open research at Oxford <br> round 1: PGR - 12 jan 2021 to 1 march 2021"
author: "Malika Ihle"
date: "01/03/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Keeping track of decisions
#### I have not considered non pgr entries
#### if one item not scored in a grid, I remove those NAs for calculation of percentage for each responses for that item. (i.e. like if items were independants)
#### for Barriers: select items if at least one answer is not NA to calculate percentages (like if items were independents)


## Sample sizes
```{r, echo = FALSE, include = FALSE}
source("Sample-sizes.R")
```

```{r, echo = FALSE}
sst
```

## Awareness
```{r, echo = FALSE, include = FALSE}
source("Awareness.R")
```

```{r, echo = FALSE, fig.width=10, fig.height=4, fig.align = "center"}
All_pgrdata_Awareness_plot
```

```{r, echo = FALSE, warning = FALSE, fig.width=10, fig.height=8, fig.align = "center"}
pgrdata_Awareness_plot
```

## Overall effect
```{r, echo = FALSE, include = FALSE}
source("Effect.R")
```

```{r, echo = FALSE, fig.width=10, fig.height=4, fig.align = "center"}
All_pgrdata_Effect_plot
```

```{r, echo = FALSE, warning = FALSE, fig.width=10, fig.height=8, fig.align = "center"}
pgrdata_Effect_plot
```

## Barriers
```{r, echo = FALSE, include = FALSE}
source("Barriers.R")
```

```{r, echo = FALSE, fig.width=10, fig.height=4, fig.align = "center"}
All_pgrdata_Barriers_plot
```

```{r, echo = FALSE, warning = FALSE, fig.width=10, fig.height=8, fig.align = "center"}
pgrdata_Barriers_plot
```

## Downsides
```{r, echo = FALSE, include = FALSE}
source("Downsides.R")
```

```{r, echo = FALSE, fig.width=10, fig.height=4, fig.align = "center"}
All_pgrdata_Downsides_plot
```

```{r, echo = FALSE, warning = FALSE, fig.width=10, fig.height=8, fig.align = "center"}
pgrdata_Downsides_plot
```

## Training
```{r, echo = FALSE, include = FALSE}
source("Training.R")
```

```{r, echo = FALSE, fig.width=10, fig.height=4, fig.align = "center"}
All_pgrdata_Training_plot
```

```{r, echo = FALSE, warning = FALSE, fig.width=10, fig.height=8, fig.align = "center"}
pgrdata_Training_plot
```

## Support
```{r, echo = FALSE, include = FALSE}
source("Support.R")
```

```{r, echo = FALSE, fig.width=10, fig.height=4, fig.align = "center"}
All_pgrdata_Support_plot
```

```{r, echo = FALSE, warning = FALSE, fig.width=10, fig.height=8, fig.align = "center"}
pgrdata_Support_plot
```
